---
output:
  html_document:
    df_print: paged
    fig.align: center
    self_contained: yes 
    fig.height: 4
    fig.width: 8
    theme: united
    toc: yes
    toc_depth: 4
    toc_float: yes
    number_sections: yes
    code_folding: hide
title: "Auswertung TC Daten"
author: "David Lilek"
date: "`r format(Sys.time(), '%d %B %Y, %X')`"
editor_options: 
  markdown: 
    wrap: 72
---



# Load Libraries & Plot function & Colors

```{r message=FALSE, warning=FALSE}
library(ggplot2)
library(tidyverse)
library(dplyr)
library(UpSetR)
library(pheatmap)
library(ggvenn)
library(knitr)
library(reshape2)
library(eulerr)
#library(venneuler)
#library(VennDiagram) 
```

```{r}
euler_venn_2comp <- function(lst, label_venn, color_venn, cex_venn, grid, gList, h_just, v_just) {
  ######################################
  #################plot 2 venn diagrams
  ######################################
  p<-plot(euler(lst),
          input="union",
          shape="ellipse",
          quantities=list(type = c("percent", 'counts'),
                          cex = cex_venn), #schriftgröße für A, B bzw intersection
          key=TRUE,
          labels=FALSE,
          lty = c(1,1),
          legend = list(labels = label_venn,
                        side = "bottom",
                        nrow = 3, ncol = 1),
          edges=TRUE,
          fills = color_venn, #color für A,B bzw intersection 
          alpha=1)
  # https://stackoverflow.com/questions/75177293/how-to-change-the-label-position-when-plotting-venn-diagram-from-eulerr-package
  tags <- p$children[[2]]$children[[1]]$children$tags$children
  tags <- do.call(grid::gList, lapply(tags, function(x) {
    x$children[[2]]$label <- sub(" \\(", "\n(", x$children[[2]]$label)
    x$children[[2]]$just <- NULL
    x$children[[2]]$hjust <- h_just
    x$children[[2]]$vjust <- v_just
    x}))
  
  p$children[[2]]$children[[1]]$children$tags$children <- tags
  print(p)
}


euler_venn_3comp <- function(lst, cex_venn, label_venn, color_venn, grid, gList, h_just, v_just) {
  ##################################
  ###### venn diagram 3 comparisons
  ##################################
  p<-plot(euler(lst),
          input="union",
          shape="ellipse",
          quantities=list(type = c("percent", 'counts'),
                          cex = cex_venn), #schriftgröße für A, B, C bzw intersection
          key=TRUE,
          labels=FALSE,
          lty = c(1,1,1),
          legend = list(labels = label_venn,
                        side = "bottom",
                        nrow = 3, ncol = 1),
          edges=TRUE,
          fills = color_venn, #color für A,B bzw intersection fills = grey[c(10,18,25)]
          alpha=1)
  # https://stackoverflow.com/questions/75177293/how-to-change-the-label-position-when-plotting-venn-diagram-from-eulerr-packages
  tags <- p$children[[2]]$children[[1]]$children$tags$children
  tags <- do.call(grid::gList, lapply(tags, function(x) {
    x$children[[2]]$label <- sub(" \\(", "\n(", x$children[[2]]$label)
    x$children[[2]]$just <- NULL
    x$children[[2]]$hjust <- h_just
    x$children[[2]]$vjust <- v_just
    x}))
  
  p$children[[2]]$children[[1]]$children$tags$children <- tags
  print(p)
}

```

## colors

```{r}
#get colors
#total protein extract
total <- rgb(255,93,93, maxColorValue = 255)
#fractions high MW SEC
highMW <- rgb(169,208,142,maxColorValue = 255)
#fractions low MW SEC
lowMW <- rgb(255,217,102, maxColorValue = 255)
#in-gel digest
IG <- rgb(180,198,231,maxColorValue = 255)



```

```{r eval=FALSE, warning=FALSE, include=FALSE}
#v001


#col X - D1
#dark: total protein extract
#light: fractionation
col_X_dark <- rgb(255,0,0, maxColorValue = 255)
col_X_light <- rgb(255,102,102,maxColorValue = 255)
#fractions high MW SEC
col_X_lowMW  <- rgb(255,153,153,maxColorValue = 255)
#fractions low MW SEC
col_X_highMW <- rgb(255,204,204, maxColorValue = 255)
col_X_carbonate <- rgb(255,170,170, maxColorValue = 255)
# D2
col_Y_light <- rgb(102,102,255, maxColorValue = 255)
col_Y_dark <- rgb(0,0,255, maxColorValue = 255)

```

```{r}
#v002


#col X - D1
#dark: total protein extract
#light: fractionation
col_X_dark <- rgb(204,0,0, maxColorValue = 255)
col_X_light <- rgb(255,70,70,maxColorValue = 255)
#fractions high MW SEC
col_X_lowMW  <- rgb(255,150,150,maxColorValue = 255)
#fractions low MW SEC
col_X_highMW <- rgb(255,230,230, maxColorValue = 255)
col_X_carbonate <- rgb(255,170,170, maxColorValue = 255)
# D2
col_Y_dark <- rgb(0,0,204, maxColorValue = 255)
col_Y_light <- rgb(70,70,255, maxColorValue = 255)

```


```{r}
#v003


#col X - D1
#dark: total protein extract
#light: fractionation
col_X_dark <- rgb(204,0,0, maxColorValue = 255)
col_X_light <- rgb(255,100,100,maxColorValue = 255)
#fractions high MW SEC
col_X_lowMW  <- rgb(255,150,150,maxColorValue = 255)
#fractions low MW SEC
col_X_highMW <- rgb(255,230,230, maxColorValue = 255)
col_X_carbonate <- rgb(255,170,170, maxColorValue = 255)
# D2
col_Y_dark <- rgb(0,0,204, maxColorValue = 255)
col_Y_light <- rgb(100,100,255, maxColorValue = 255)

```

```{r eval=FALSE, include=FALSE}
#v004

#https://r-charts.com/color-palettes/
#paletteer_c("ggthemes::Red-Blue Diverging", 30)
#col X - D1
#dark: total protein extract
#light: fractionation
col_X_dark <- "#A90C38"
col_X_light <- "#EB5C52"
#fractions high MW SEC
col_X_lowMW  <- "#ECBBB0"
#fractions low MW SEC
col_X_highMW <- "#E4CCC6"
col_X_carbonate <- rgb(255,170,170, maxColorValue = 255)
# D2
col_Y_dark <- "#2E7A85"
col_Y_light <- "#78A8CE"

```

# Grafik 0 - Puffervergleich

```{r message=FALSE, warning=FALSE, fig.width=4,fig.height=4}
# Siehe Proteinquanti_Puffervergleich.xlsx -> Teams 
values <- c(6.39,
            6.09,
            12.33,
            10.68,
            15.1,
            14.12)
puffer <- c("Citrate","Citrate","Phosphate","Phosphate","Carbonate","Carbonate")
data <- as.data.frame(cbind(values,puffer))

res <- aov(values ~ puffer, data = data)
summary(res)
TukeyHSD(res)

#puffer <- factor(puffer, levels = c("Citrat", "Phosphate", "Carbonate"))
data_4plot <- as.data.frame(cbind(values, factor(puffer)))
ggplot(data_4plot, aes(x=reorder(puffer,values), y=values)) + 
  geom_boxplot() + 
  labs(x = "",
       y = "Protein concentration mg/mL") +
  scale_x_discrete(labels = c("Citrate" = "Citrate", "Phosphate" = "Phosphate", "Carbonate" = "Carbonate"))

res_raw <- readRDS(file = "results_v002/mqpar_extracts_2gether_reanalysisCM_extraktejakob_proteinGroups.txt_Unique.RDS")
res_raw <- res_raw[[1]]


res <- res_raw[,-ncol(res_raw)]
res <- res*1

CAR <- apply(res[,c(1:2)], 1, any)
CIT <- apply(res[,c(3:4)],1,any)
PHOS <- apply(res[,c(5:6)],1,any)

fasta <- c()
for (i in 1:length(res_raw$FASTA)){
  tmp <- strsplit(res_raw$FASTA[i],split='\\|')[[1]][2]
  fasta <- c(fasta,tmp)
}

res_clear <- as.data.frame(cbind(CAR,CIT,PHOS,fasta))

res_clear$CAR <- as.logical(res_clear$CAR)
res_clear$CIT <- as.logical(res_clear$CIT)
res_clear$PHOS <- as.logical(res_clear$PHOS)
res_clear <- res_clear[,-4]*1
res_clear[res_clear==0] <- NA



proteins <- as.data.frame(which(!is.na(res_clear), arr.ind=TRUE))

CAR <- proteins %>% dplyr::filter(col == 1)
CIT <- proteins %>% dplyr::filter(col == 2)
PHOS <- proteins %>% dplyr::filter(col == 3)

# combine to list
lst <- list("CIT"=as.double(CIT[,1]),
            "PHOS"=as.double(PHOS[,1]),
            "CAR"=as.double(CAR[,1]))
            


#venn digarams
#get colors
col1 <- rgb(255,93,93, maxColorValue = 255)
#fractions high MW SEC
col2 <- rgb(169,208,142,maxColorValue = 255)
#fractions low MW SEC
col3 <- rgb(255,217,102, maxColorValue = 255)

euler_venn_3comp(lst, label_venn = c("Citrate buffer pH 4.8", "Phosphate buffer pH 8","Carbonate buffer pH 10.8"),
                 color_venn = c(col2,col_X_dark,col3), cex_venn = c(1,1,0.70,0.9,0,1,1), h_just = 0.5, v_just = 0.5)
```


# Grafik 1 - Comparison E3_D1 - noTreatment, Heatshock, ProteaseInhibitor

The results show that the significant highest number of protein identifications (median=586) could be achieved using protease inhibitor. The significant lowest number of proteins was determined using heatshock (median=315). No treatment resulted in 491 identified proteins. (p value ANOVA 1.43e-09; p value Tukey HSD test below 0.0003). All measurement were performed in using 6 technical replicates.


ACHTUNG: Die Anzahl der oben genannten Proteine beziehen sich auf die Bildung des einfachen Mittelwertes. Hier wenn man merged und die "wirkliche" Anzahl an Proteinen gibt.

```{r message=FALSE, warning=FALSE, fig.width=4,fig.height=4}
#E3_D1
D1_raw <- readRDS(file = "results_v002/results_run1_mqpar_extracts_2gether_E3_D1_LFQ_combined_txt_proteinGroups.txt_Unique.RDS")
D1_raw <- D1_raw[[1]]

D1 <- D1_raw[,-ncol(D1_raw)]
D1 <- D1*1

noT <- apply(D1[,c(1:6)], 1, any)
HS <- apply(D1[,c(7:12)],1,any)
PI <- apply(D1[,c(13:18)],1,any)
print("no Treatment")
sum(noT*1)
print("Heatshock")
sum(HS*1)
print("Protease Inhibitor")
sum(PI*1)
```

```{r, fig.width=4,fig.height=4}
data <- read.csv("Extraktionen_gesamt_V2_DL.csv", sep=";")
data_sub <- as.data.frame(data$Unique.no.MBR.2.peptides)
data_sub <- as.data.frame(data_sub[c(1:18),])
data_sub$group <- c(rep("No treatment",6),
                   rep("Heatshock",6),
                   rep("Protease inhibitor",6))
colnames(data_sub) <- c("number","group")
print("Median and sd no Treatment")
median(subset(data_sub,group=="No treatment")[,1])
sd(subset(data_sub,group=="No treatment")[,1])
print("Median and sd Heatshock")
median(subset(data_sub,group=="Heatshock")[,1])
sd(subset(data_sub,group=="Heatshock")[,1])
print("Median and sd ProteaseInhibitor")
median(subset(data_sub,group=="Protease inhibitor")[,1])
sd(subset(data_sub,group=="Protease inhibitor")[,1])
ggplot(data_sub, aes(x=group, y=number)) + 
  geom_boxplot() +
  theme(axis.title.x = element_blank())
anova <- aov(number ~ group, data=data_sub)
summary(anova)
Tukey <- TukeyHSD(anova)
plot(Tukey)
Tukey
```

# Grafik 2

## A

```{r, fig.width=4,fig.height=4}
# D1-D2 comparison

D1_raw <- readRDS(file = "results_v002/results_run1_mqpar_extracts_2gether_E4_D1_a-j_LFQ_combined_txt_proteinGroups.txt_Unique.RDS")
D1_raw <- D1_raw[[1]]
D1 <- dplyr::select(D1_raw, contains("Pool"))
D1 <- apply(D1, 1, any)
#D1 <- as.data.frame(cbind(D1, D1_raw$FASTA))
fasta <- c()
for (i in 1:length(D1_raw$FASTA)){
  tmp <- strsplit(D1_raw$FASTA[i],split='\\|')[[1]][2]
  fasta <- c(fasta,tmp)
}
D1 <- as.data.frame(cbind(D1, fasta))
D2_raw <- readRDS(file = "results_v002/results_run1_mqpar_extracts_2gether_D2_LFQ_combined_txt_proteinGroups.txt_Unique.RDS")
D2_raw <- D2_raw[[1]]
D2 <- dplyr::select(D2_raw, contains("Gesamt"))
D2 <- apply(D2, 1, any)
fasta <- c()
for (i in 1:length(D2_raw$FASTA)){
  tmp <- strsplit(D2_raw$FASTA[i],split='\\|')[[1]][2]
  fasta <- c(fasta,tmp)
}
#D2 <- as.data.frame(cbind(D2, D2_raw$FASTA))
D2 <- as.data.frame(cbind(D2, fasta))
D1_D2_comparison  <- merge(D1, D2,
                           all = TRUE,
                           by = "fasta")

D1_D2_comparison$D1 <- as.logical(D1_D2_comparison$D1)
D1_D2_comparison$D2 <- as.logical(D1_D2_comparison$D2)
D1_D2_comparison <- D1_D2_comparison[,-1]*1
D1_D2_comparison[D1_D2_comparison==0] <- NA



proteins <- as.data.frame(which(!is.na(D1_D2_comparison), arr.ind=TRUE))

D1_inter <- proteins %>% dplyr::filter(col == 1)
D2_inter <- proteins %>% dplyr::filter(col == 2)

# combine to list
lst <- list("E4_D1"=as.double(D1_inter[,1]),
            "E4_D2"=as.double(D2_inter[,1]))






euler_venn_2comp(lst, label_venn = c("D1: Phosphate buffer", "D2: Phosphate buffer with urea-triton X"), color_venn = c(col_X_dark, col_Y_dark), cex_venn = c(1,1), h_just = 0.5, v_just = 0.5)


print(c("E4_D1","E4_D2"))
sum(D1_D2_comparison$D1,na.rm = TRUE)
sum(D1_D2_comparison$D2,na.rm = TRUE)
```


## B

```{r, fig.width=4,fig.height=4}
data <- readRDS("./27_20230201_FH/results/D5_extracts_Razor.RDS")
data <- data[[1]]
b <- dplyr::select(data, contains("_b"))
D1_b <- b$Razor...unique.peptides.1_b_01+ b$Razor...unique.peptides.1_b_02
D2_b <- b$Razor...unique.peptides.2_b_01 + b$Razor...unique.peptides.2_b_02
D4_b <- b$Razor...unique.peptides.4_b_01 + b$Razor...unique.peptides.4_b_02
b <- as.data.frame(cbind(D1_b,D2_b,D4_b))
b[b==0] <- NA
b[b==2] <- 1

#venn diagram
proteins <- as.data.frame(which(!is.na(b), arr.ind=TRUE))
D1_b <- proteins %>% dplyr::filter(col == 1)
D2_b <- proteins %>% dplyr::filter(col == 2)
D4_b <- proteins %>% dplyr::filter(col == 3)

# combine to list
lst <- list(E5_D1_b = as.double(D1_b[,1]),
            E5_D2_b = as.double(D2_b[,1]),
            E5_D4_b = as.double(D4_b[,1]))


euler_venn_3comp(lst, label_venn = c("D1: Phosphate buffer",
                                     "D1b: Carbonate buffer",
                                     "D2: Phosphate buffer with urea-triton X"), 
                 color_venn = c(col_X_dark,
                                col3,
                                col_Y_dark), 
                 cex_venn = c(1,1,1,1,0,1,1),
                 h_just = 0.5, v_just = 0.5)

print(c("E5_D1_b","E5_D2_b","E5_D4_b"))
sum(b$Razor...unique.peptides.1_b_01,na.rm = TRUE)
sum(b$Razor...unique.peptides.2_b_01,na.rm = TRUE)
sum(b$Razor...unique.peptides.4_b_01,na.rm = TRUE)
```




## C

```{r, fig.width=8,fig.height=4,message=FALSE, warning=FALSE}
# D1-D2 comparison
D1_raw <- readRDS(file = "results_v002/results_run1_mqpar_extracts_2gether_E4_D1_a-j_LFQ_combined_txt_proteinGroups.txt_Unique.RDS")
D1_raw <- D1_raw[[1]]
D1 <- dplyr::select(D1_raw, contains("Pool"))
D1 <- apply(D1, 1, any)
#D1 <- as.data.frame(cbind(D1, D1_raw$FASTA))
fasta <- c()
for (i in 1:length(D1_raw$FASTA)){
  tmp <- strsplit(D1_raw$FASTA[i],split='\\|')[[1]][2]
  fasta <- c(fasta,tmp)
}
D1 <- as.data.frame(cbind(D1, fasta))
D2_raw <- readRDS(file = "results_v002/results_run1_mqpar_extracts_2gether_D2_LFQ_combined_txt_proteinGroups.txt_Unique.RDS")
D2_raw <- D2_raw[[1]]
D2 <- dplyr::select(D2_raw, contains("Gesamt"))
D2 <- apply(D2, 1, any)
fasta <- c()
for (i in 1:length(D2_raw$FASTA)){
  tmp <- strsplit(D2_raw$FASTA[i],split='\\|')[[1]][2]
  fasta <- c(fasta,tmp)
}
#D2 <- as.data.frame(cbind(D2, D2_raw$FASTA))
D2 <- as.data.frame(cbind(D2, fasta))
D1_D2_comparison  <- merge(D1, D2,
                           all = TRUE,
                           by = "fasta")
D1_D2_comparison$comb <- apply(D1_D2_comparison[,c(2:3)], 1, any)
#E5
data <- readRDS("./27_20230201_FH/results/D5_extracts_Razor.RDS")
data <- data[[1]]
b <- dplyr::select(data, contains("_b"))
b <- b[,-c(5:6)]
b <- as.data.frame(apply(b, 1, any))
fasta <- c()
for (i in 1:length(data$FASTA)){
  tmp <- strsplit(data$FASTA[i],split='\\|')[[1]][2]
  fasta <- c(fasta,tmp)
}
b$fasta <- fasta
colnames(b) <- c("b","fasta")

#merge with D5
D1_D2_D5_comparison  <- merge(D1_D2_comparison[,c(1,4)],b,
                           all = TRUE,
                           by = "fasta")
colnames(D1_D2_D5_comparison) <- c("fasta","E4","E5")

D1_D2_D5_comparison$D1 <- as.logical(D1_D2_D5_comparison$E4)
D1_D2_D5_comparison$D2 <- as.logical(D1_D2_D5_comparison$E5)
D1_D2_D5_comparison <- D1_D2_D5_comparison[,-1]*1
D1_D2_D5_comparison[D1_D2_D5_comparison==0] <- NA



proteins <- as.data.frame(which(!is.na(D1_D2_D5_comparison), arr.ind=TRUE))

E4_inter <- proteins %>% dplyr::filter(col == 1)
E5_inter <- proteins %>% dplyr::filter(col == 2)


# combine to list
lst <- list("2D"=as.double(E4_inter[,1]),
            "3D"=as.double(E5_inter[,1]))

upset(fromList(lst), 
      order.by = "freq",
      nsets = 10,
      nintersects = 15,
      keep.order = TRUE,
      sets=c("2D", "3D"),
      mainbar.y.label = "Number of shared proteins",
      sets.x.label = "Number of proteins per fraction",
      set_size.show = TRUE,
      set_size.angles = 0,
      set_size.scale_max = 1500
)


       
```




# Grafik 3

## A

```{r, fig.width=4,fig.height=4}

############## B
data <- readRDS(file = "results_v002/results_run1_mqpar_extracts_2gether_E4_D1_B_LFQ_combined_txt_proteinGroups.txt_Unique.RDS")
data <- data[[1]]
data_sub <- dplyr::select(data, contains("Pool_G"))
#get rid of FALSE values
B <- data_sub*1
B[B==0] <- NA
ind <- apply(B, 1, function(x) all(is.na(x)))


############AF
data <- readRDS(file = "results_v002/results_run1_mqpar_extracts_2gether_E4_D1_AF_TF_LFQ_combined_txt_proteinGroups.txt_Unique.RDS")
data <- data[[1]]
data_sub <- dplyr::select(data, contains("Pool_AF"))
#get rid of FALSE values
AF <- data_sub*1
AF[AF==0] <- NA
ind <- apply(AF, 1, function(x) all(is.na(x)))

############TF
data <- readRDS(file = "results_v002/results_run1_mqpar_extracts_2gether_E4_D1_AF_TF_LFQ_combined_txt_proteinGroups.txt_Unique.RDS")
data <- data[[1]]
data_sub <- dplyr::select(data, contains("Pool_TF"))
#get rid of FALSE values
TF <- data_sub*1
TF[TF==0] <- NA
ind <- apply(TF, 1, function(x) all(is.na(x)))


## compare AF TF B poster
AF_TF_raw <- readRDS(file = "results_v002/results_run1_mqpar_extracts_2gether_E4_D1_AF_TF_LFQ_combined_txt_proteinGroups.txt_Unique.RDS")
AF_TF_raw <- AF_TF_raw[[1]]
AF <- dplyr::select(AF_TF_raw, contains("AF"))
AF <- apply(AF, 1, any)
fasta <- c()
for (i in 1:length(AF_TF_raw$FASTA)){
  tmp <- strsplit(AF_TF_raw$FASTA[i],split='\\|')[[1]][2]
  fasta <- c(fasta,tmp)
}
AF <- as.data.frame(cbind(AF, fasta))
TF <- dplyr::select(AF_TF_raw, contains("TF"))
TF <- apply(TF, 1, any)
TF <- as.data.frame(cbind(TF, fasta))
B_raw <- readRDS(file = "results_v002/results_run1_mqpar_extracts_2gether_E4_D1_B_LFQ_combined_txt_proteinGroups.txt_Unique.RDS")
B_raw <- B_raw[[1]]
B <- dplyr::select(B_raw, contains("Pool_G"))
B <- apply(B, 1, any)
fasta <- c()
for (i in 1:length(B_raw$FASTA)){
  tmp <- strsplit(B_raw$FASTA[i],split='\\|')[[1]][2]
  fasta <- c(fasta,tmp)
}
B <- as.data.frame(cbind(B, fasta))

AF_TF_B_comparison  <- merge(B, AF,
                           all = TRUE,
                           by = "fasta")
AF_TF_B_comparison <- merge(AF_TF_B_comparison, TF,
                            all = TRUE,
                            by = "fasta")

AF_TF_B_comparison$B <- as.logical(AF_TF_B_comparison$B)
AF_TF_B_comparison$AF <- as.logical(AF_TF_B_comparison$AF)
AF_TF_B_comparison$TF <- as.logical(AF_TF_B_comparison$TF)
AF_TF_B_comparison <- AF_TF_B_comparison[,-1]*1
AF_TF_B_comparison[AF_TF_B_comparison==0] <- NA




proteins <- as.data.frame(which(!is.na(AF_TF_B_comparison), arr.ind=TRUE))

B <- proteins %>% dplyr::filter(col == 1)
AF <- proteins %>% dplyr::filter(col == 2)
TF <- proteins %>% dplyr::filter(col == 3)


# combine to list
lst <- list("E4_D1_B"=as.double(B[,1]),
            "E4_D1_AF"=as.double(AF[,1]),
            "E4_D1_TF"=as.double(TF[,1]))







euler_venn_3comp(lst, 
                 label_venn = c("D1-electrophoretic fractionation","D1-low MW SEC fractionation","D1-high MW SEC fractionation"),
                 color_venn = c(col_X_light, col_X_lowMW, col_X_highMW), 
                 cex_venn = c(1,
                              0.7,
                              0.5,
                              0.8,
                              0.8,
                              0.6,
                              1),
                 h_just = 0.5,
                 v_just = 0.5)

print(c("E4_D1_B","E4_D1_AF","E4_D1_TF"))
sum(AF_TF_B_comparison$B,na.rm = TRUE)
sum(AF_TF_B_comparison$AF,na.rm = TRUE)
sum(AF_TF_B_comparison$TF,na.rm = TRUE)
        


```

## B

```{r, fig.width=4,fig.height=4}
#compare B to pool from 0609 
B_raw <- readRDS(file = "results_v002/results_run1_mqpar_extracts_2gether_E4_D1_B_LFQ_combined_txt_proteinGroups.txt_Unique.RDS")
B_raw <- B_raw[[1]]
B <- dplyr::select(B_raw, contains("Pool_G"))
B <- apply(B, 1, any)
fasta <- c()
for (i in 1:length(B_raw$FASTA)){
  tmp <- strsplit(B_raw$FASTA[i],split='\\|')[[1]][2]
  fasta <- c(fasta,tmp)
}
B <- as.data.frame(cbind(B, fasta))
aj_raw <- readRDS(file = "results_v002/results_run1_mqpar_extracts_2gether_E4_D1_a-j_LFQ_combined_txt_proteinGroups.txt_Unique.RDS")
aj_raw <- aj_raw[[1]]
aj <- dplyr::select(aj_raw, contains("Pool"))
aj <- apply(aj, 1, any)
fasta <- c()
for (i in 1:length(aj_raw$FASTA)){
  tmp <- strsplit(aj_raw$FASTA[i],split='\\|')[[1]][2]
  fasta <- c(fasta,tmp)
}
aj <- as.data.frame(cbind(aj, fasta))
B_aj_comparison  <- merge(B, aj,
                             all = TRUE,
                             by = "fasta")

B_aj_comparison$B <- as.logical(B_aj_comparison$B)
B_aj_comparison$aj <- as.logical(B_aj_comparison$aj)
B_aj_comparison <- B_aj_comparison[,-1]*1
B_aj_comparison[B_aj_comparison==0] <- NA


proteins <- as.data.frame(which(!is.na(B_aj_comparison), arr.ind=TRUE))

B_inter <- proteins %>% dplyr::filter(col == 1)
aj_inter <- proteins %>% dplyr::filter(col == 2)

# combine to list
lst <- list("E4_D1_B_fractions"=as.double(B_inter[,1]),
            "E4_D1"=as.double(aj_inter[,1]))





euler_venn_2comp(lst, label_venn = c("D1-electrophoretic fractionation","D1-total protein extract"), color_venn = c(col_X_light, col_X_dark), cex_venn = c(1,0.6,1), h_just = 0.5, v_just = 0.5)

print(c("B","E4_D1_pool"))
sum(B_aj_comparison$B,na.rm = TRUE)
sum(B_aj_comparison$aj,na.rm = TRUE)
       

```


## C

```{r, fig.width=4,fig.height=4}
#############################
# D2
###############################
data <- readRDS(file = "results_v002/results_run1_mqpar_extracts_2gether_D2_LFQ_combined_txt_proteinGroups.txt_Unique.RDS")
data <- data[[1]]
data_sub <- dplyr::select(data, contains("Pool_20"))
B_D2 <- data_sub*1
B_D2[B_D2==0] <- NA


### analysis B
proteins <- as.data.frame(which(!is.na(B_D2), arr.ind=TRUE))

B1 <- proteins %>% dplyr::filter(col == 1 ) # | col == 2 -> means or col2
B10 <- proteins %>% dplyr::filter(col == 2)
B2 <- proteins %>% dplyr::filter(col == 3)
B3 <- proteins %>% dplyr::filter(col == 4)
B4 <- proteins %>% dplyr::filter(col == 5)
B5 <- proteins %>% dplyr::filter(col == 6)
B6 <- proteins %>% dplyr::filter(col == 7)
B7 <- proteins %>% dplyr::filter(col == 8)
B8 <- proteins %>% dplyr::filter(col == 9)
B9 <- proteins %>% dplyr::filter(col == 10)
# combine to list
lst <- list(B1 = as.double(B1[,1]),
            B2 = as.double(B2[,1]),
            B3 = as.double(B3[,1]),
            B4 = as.double(B4[,1]),
            B5 = as.double(B5[,1]),
            B6 = as.double(B6[,1]),
            B7 = as.double(B7[,1]),
            B8 = as.double(B8[,1]),
            B9 = as.double(B9[,1]),
            B10 = as.double(B10[,1]))            


data_D2_pool <- dplyr::select(data, contains("Gesamt"))
data_D2_pool <- apply(data_D2_pool, 1, any)
data_D2_fractions <- dplyr::select(data, contains("20"))
data_D2_fractions <- apply(data_D2_fractions, 1, any)
data_D2 <- as.data.frame(cbind(data_D2_pool,data_D2_fractions))
data_D2 <- data_D2*1
data_D2[data_D2==0] <- NA



proteins <- as.data.frame(which(!is.na(data_D2), arr.ind=TRUE))

D2_pool_inter <- proteins %>% dplyr::filter(col == 1)
D2_fractions_inter <- proteins %>% dplyr::filter(col == 2)

# combine to list
lst <- list(D2_fractions=as.double(D2_fractions_inter[,1]),
            D2_pool=as.double(D2_pool_inter[,1]))

#venn digarams
#get colors
D2_pool_col <- rgb(255,93,93, maxColorValue = 255)
D2_ingel_col <- rgb(169,208,142,maxColorValue = 255)
#E4_D1_pool_col <- rgb(255,217,102, maxColorValue = 255)


euler_venn_2comp(lst, label_venn = c("D2-electrophoretic fractionation","D2-total protein extract"), color_venn = c( col_Y_light,col_Y_dark), cex_venn = c(1,0.6,1), h_just = 0.5, v_just = 0.5)

```



# Grafik 4

## E4_D1

* manuell von hier abgeschrieben `file://fhwn.ac.at/TU/Forschung/wissenschaftliche%20Ver%C3%B6ffentlichungen/Publikationen/2022/Proteomics_JRS_DL/data/evaluation_summary.html#4_Compare_D1_and_D2_B1-B9_resp_B1-B10`

```{r, fig.width=4,fig.height=4}
#col <- rgb(98,90,189, maxColorValue = 255)
#col <- rgb(87,83,148, maxColorValue = 255)
#col <- rgb(142,136,200, maxColorValue = 255)
#col <- rgb(146,146,233, maxColorValue = 255)
dat <- as.data.frame(
  cbind(c(126,159,147,241,322,591,661,852,699),
        c(paste("B",1:9,sep=""))))
colnames(dat) <- c("no","fraction")
dat$no <- as.numeric(dat$no)

positions <-  c(paste("B",9:1,sep=""))


ggplot(data=dat, aes(x=fraction,y=no))+
  geom_bar(stat="identity") +#fill=col
  coord_flip() +
  geom_text(aes(label=no), hjust=1.5,vjust=0.6, color="white", size=4) +
  theme(axis.title.y = element_blank(),axis.text.y = element_text(size=14)) + 
  scale_y_continuous(breaks = seq(0, 1000, by = 100)) +
  labs(y="Number of proteins per fraction") +
  scale_x_discrete(limits = positions)
```

## E4_D2

* manuell von hier abgeschrieben `file:///X:/wissenschaftliche%20Ver%C3%B6ffentlichungen/Publikationen/2022/Proteomics_JRS_DL/data/evaluation_summary_4publication.html#9_D2`

```{r, fig.width=4,fig.height=4}
dat <- as.data.frame(
  cbind(c(107,241,231,142,145,148,139,166,180,98),
        c(paste("B",1:10,sep=""))))
colnames(dat) <- c("no","fraction")
dat$no <- as.numeric(dat$no)

positions <-  c(paste("B",10:1,sep=""))

ggplot(data=dat, aes(x=fraction,y=no))+
  geom_bar(stat="identity") +
  coord_flip() +
  geom_text(aes(label=no), hjust=1.5,vjust=0.6, color="white", size=4) +
  theme(axis.title.y = element_blank(),axis.text.y = element_text(size=14)) + 
  scale_y_continuous(breaks = seq(0, 1000, by = 100)) +
  scale_x_discrete(limits = positions) +
  labs(y="Number of proteins per fraction")
```



